\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 intro.tex
.

In \cite{zutshi2014multiple}, the authors investigate an on-the-fly
abstraction technique that is close to the approach we propose. A key
difference is that the abstraction explored in this work is an {\em
existential} abstraction: the approximate model learned is a directed
acyclic graph, where nodes represent regions of the state-space, and
an edge between two regions indicates that there is a transition
between some states in the regions. Our approach can be viewed as a
further improvement of the existential abstraction by annotating an
edge in the graph-based abstraction with an affine relation between
the source and destination states connected by the edge.

>>>>

In \cite{zutshi2014multiple}, the authors investigate an on-the-fly
abstraction technique that is close to the approach we propose. A key
difference is that the abstraction explored in this work is an
existential {\em relational} abstraction. The approximate model
learned is a directed acyclic graph, where nodes represent regions of
the state-space, and an edge between two regions indicates a
transition between states in the regions. Our approach further
improves the existential abstraction by annotating the edges in the
graph-based abstraction with affine relations between the source and
destination states.
